DataGatheringandAnalysis

### 2014-11-11 GEMDataSource.Rmd
Added cache = false for repository data

# Import fear of failure data
FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = TRUE)

# Import current owner data
CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = TRUE)

# Import entrepreneurial intention data
EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = TRUE)

# Import nascent entrepreneur data
NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = TRUE)

# Import perceived capabilities data
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = TRUE)

>>>>

# Import fear of failure data
FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)

# Import current owner data
CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)

# Import entrepreneurial intention data
EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)

# Import nascent entrepreneur data
NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)

# Import perceived capabilities data
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)
